### 2024-11-18 conteudo/preliminar/results.tex
minor changes on the feedback process

The refactoring of the second function pair, however, was successful. 
We submitted this refactoring as a patch to the AMD Display driver to obtain feedback 
from the maintainers.

The process of sending the patch did not yield satisfactory results in terms of 
interaction with the AMD Display driver maintainers. We initially submitted the 
patch on August 9th, 2024, but did not receive any replies. As a result, we had 
to resend it on October 9th, 2024, and finally received an initial response on 
November 3rd, 2024, from our point of contact at the AMD Display driver. 
The response time from our interactions with the AMD Display driver is making 
us reconsider the viability of our initial plans.

@@

\todo[inline]{Atualizar ... tentar colocar algo do feedback que recebeu da revisão do patch}

\input{conteudo/preliminar/cronograma}
\todo[inline]{Atualizar o cronograma, alocando tempo para evolucao da ferramenta (DONE?) }

>>>>

The refactoring of the second function pair, however, was successful. We submitted this refactoring as a patch to the AMD Display driver to obtain feedback from the maintainers. The process of sending the patch took more time than expected. We initially submitted the patch on August 9th, 2024, but we did not receive replies. As a result, we had to resend it on October 9th, 2024 and received an initial response on November 3rd, 2024.

We understood new details about the driver evolution processes in discussions with our partner from the AMD Display driver. Some of the code in the driver is shared across all operating systems that support the implemented GPUs. This fact creates a complex process within AMD to format and submit changes across the supported systems while simultaneously implementing measures to mitigate errors.

Additionally, we comprehended that AMD Display driver developers can not view duplicated code negatively, as we understand it is a good practice in software engineering. One example shared with us is that duplicated code enhances the independence of GPU driver code, allowing developers to make changes to a specific GPU without needing to test compatibility with others. This approach helps save significant time and effort.

@@

\input{conteudo/preliminar/cronograma}
